Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-06 manuscript/manuscript.tex
Fixed a few formatting issues.

\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% first the title is needed
\title{Identifiyng Inter-Genomic Repeats Using Fast, Approximate Betweenness Centrality}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jay Ghurye%
\and Chris Hill\and Mihai Pop}
%
\authorrunning{Identifiyng Inter-Genomic Repeats Using Fast,
Approximate Betweenness Centrality}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{University of Maryland, College Park\\
\mailsa\\
\mailsb\\
\mailsc\\
\url{http://www.springer.com/lncs}}

@@

>>>>

\usepackage{url}
\urldef{\mailsa}\path|{jayg, cmhill, mpop}@cs.umd.edu|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% first the title is needed
\title{Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality}

% a short form should be given in case it is too long for the running head
\titlerunning{Identifying Inter-Genomic Repeats Using Fast, Approximate Betweenness Centrality}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jay Ghurye%
\and Christopher M. Hill\and Mihai Pop}
%
\authorrunning{Identifiyng Inter-Genomic Repeats Using Fast,
Approximate Methods for Betweenness Centrality}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{University of Maryland, College Park\\
\mailsa\\}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width = \textwidth]{sampled_nodes}
\caption{Example of conversion of de Bruijn graph to Repeats graph}
\label{fig:sampled_nodes}
\end{figure}
